\TITLE

### 2023-10-27 paper/main.tex
improve introduction with additional background

Providing personal information exposes users to privacy risks, i.e. the potential loss of control over personal information \cite{smithInformationPrivacyResearch2011}.

Such personal information can be used deliberately or by accident (e.g. theft) for insider disclosure, unauthorised access or commercial gain. For example, by reselling it to marketers, financial institutions, other businesses, government agencies or even cybercriminals. 
This, in turn, can lead to unintentional GDPR or CCPA breaches, profiled advertising, or even criminal activity such as identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.

@@

The problem is compounded when personal information is linked to health records, legal documents or biological materials such as DNA, saliva or blood.
In such situations, clients may be reluctant to provide their personal information to the SP and therefore withdraw from the service. Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.

The guarantee of privacy of personal data is often based solely on trust in the SP's staff and the security of their IT systems. However, we observe that personal data is often used only for logistical purposes, such as payment or communication, and could be provided anonymously if such methods were available.

>>>>

Providing personal information exposes users to a myriad of privacy risks, ranging from the potential loss of control over personal information to more severe threats like identity theft, data breaches, and unsanctioned monitoring. Such sensitive information is highly valuable to a potential attacker as it can be exploited for insider leaks, unauthorized entry, or financial profit. For instance, this data might be sold to marketers, banks, other corporations, government bodies, or cybercriminals. Consequently, this could unintentionally violate regulations like GDPR or CCPA, result in targeted advertising, or lead to crimes such as identity theft or unlawful tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.

@@

The problem is amplified when personal information is linked to health records, legal documents or biological materials such as DNA, saliva or blood.
In such situations, clients may be reluctant to provide their personal information to the SP and therefore withdraw from the service. \textbf{Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.}

In the majority of healthcare system, the critical data managed typically resides in the Electronic Medical Records (EMRs), which is consistently regarded as confidential information requiring robust security measures~\cite{jinReviewSecurePrivacypreserving2019}~\cite{keshtaSecurityPrivacyElectronic2021}.

Mantaining the privacy of health data seems to be open and active area of reserach in the field of Privacy-Preserving Data Mining (PPDM) ~\cite{nareshPrivacyPreservingData2023,linPPSFOpensourcePrivacypreserving2018,hewagePrivacypreservingDataStream2023}. The recent reserach in this area focuses on employing methods of anonymisation and hiding sensitive information of the EMRs~\cite{hamdiEnhancingSecurityPrivacy2023, sharmaPrivacyPreservingData2019, wuHidingSensitiveInformation2021}, or securing the interaction between patient and Healthcare system~\cite{zhangPrivacyProtectionTelecare2016, mehmoodAnonymousAuthenticationScheme2018, khasimImprovedFastSecure2022}.

However, in our study, we focus on the possibility of carrying out services without revealing any personal information — solving the problem of privacy at a much earlier stage.
